\documentclass{article}

\begin{document}



\section*{Research Grants}

\begin{itemize}
\item[2006--2009] Chilean Science Foundation (FONDECYT) 

  Project: Invariant Measures and Thermodynamic Formalism for
  Meromorphic Functions (Fondecyt N. 11060538), Principal Researcher.
\item[2006--2009] Chilean Science Foundation (CONICYT) 

  Low Dimensional Dynamical Systems Network, Young Researcher.
\item[2006--2009] European Union

  Marie Curie Research Training Network CODY: Conformal Structures and
  Dynamics, Associate Researcher of Warsaw node.
\item[2005] Warsaw University of Technology

  Geometric Rigidity and Multifractal Analysis for Meromorphic
  Function.
\item[2004] Warsaw University of Technology

  Project: Investigation of Properties of the Julia Set of Functions
  of the Form $f=R(\exp(z))$, where $R$ is a Rational Map, Principal
  Researcher.
\item[2004] Warsaw University of Technology

  Project: Hausdorff Dimension and Geometry of the Julia Set for Meromorphic
  Functions.
\item[2003--2006] Polish Science Foundation (KBN)

  Project: Conformal Dynamical Systems and Geometry of the Fractal Sets.
\item[2002--2003] Warsaw University of Technology 

  project: Conformal and Invariant Measures and Hausdorff Dimension of the
  Julia Set for Transcendental Meromorphic Functions.
\item[2001] Warsaw University of Technology

  Project: Invariant Measures for Meromorphic Functions.
% \item[2000--2004] European Union

%   Marie Curie Research Training Network CALCULEMUS: Systems for
%   Integrated Computation and Deduction.
% \item[1997--1998] Polish Science Foundation (KBN)

%   Project: Natural Artificial Intelligence Research in Automated
%   Reasoning.
\end{itemize}
\end{document}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
